Sound Automated Synthesis of Digital Controllers

### 2016-10-10 paper/paper.tex
Minor changes

\begin{mylemma}{\cite{Bessa16,fadali}}
\label{internal_stab_lemma}
A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem}, with transfer functions $\hat{C}(z) = \frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and $\hat{G}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is internally stable if and only if:
\begin{itemize}
\item  the roots of characteristic polynomial $S(z)$ are inside the open unit circle, where $S(z)$ is:
\begin{equation}
\label{lemma:eq_int_stab}
S(z)=FWL[N_{C}(z)]\hat{N}_{G}(z)+FWL[D_{C}(z)]\hat{D}_{G}(z);
\end{equation}
\item the direct loop product $\frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}\cdot \frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$ has no pole-zero cancellation on or outside the unit circle;
\item the controller $\hat{C}(z)$ is a minimum-phase system. 
\end{itemize}
\end{mylemma}

@@

We use this method to check the stability in the $z$-domain for the characteristic polynomial $S(z)$ of 
the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$, where $Y(z)$ is the 
closed-loop system output and U(z) is the controller output. 
%% \red{[unclear: what matrix? We need to clarify the relationship
%% between the char. poly. $S(z)$ and the later quantities $\Delta
%% N_{G}(z), \Delta D_{G}(z)$ and corresponding controller's
%% structure.]}.
%
We consider the following form for $S(z)$:
%
$$
S(z) = a_0Z^N+a_1z^{N-1}+\cdots+a_{N-1}z+a_N=0, a_0\neq0
$$
%
%\cdsay{is this for the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$?}

>>>>

\begin{mylemma}{\cite{Bessa16,fadali}}
\label{lemma:eq_int_stab}
A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem}, with transfer functions $\hat{C}(z) = \frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and $\hat{G}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is internally stable if and only if:
\begin{itemize}
\item  the roots of characteristic polynomial $S(z)$ are inside the open unit circle, where $S(z)$ is:
\begin{equation}
\label{eq:internal_stab_lemma}
S(z)=FWL[N_{C}(z)]\hat{N}_{G}(z)+FWL[D_{C}(z)]\hat{D}_{G}(z);
\end{equation}
\item the direct loop product $\frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}\cdot \frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$ has no pole-zero cancellation on or outside the unit circle;
\item the controller $\hat{C}(z)$ is a minimum-phase system. 
\end{itemize}
\end{mylemma}

@@

We use this method to check the stability in the $z$-domain for the characteristic polynomial $S(z)$ defined in~\eqref{eq:internal_stab_lemma}.

% of the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$, where $Y(z)$ is the closed-loop system output and U(z) is the controller output. 
%% \red{[unclear: what matrix? We need to clarify the relationship
%% between the char. poly. $S(z)$ and the later quantities $\Delta
%% N_{G}(z), \Delta D_{G}(z)$ and corresponding controller's
%% structure.]}.
%
We consider the following form for $S(z)$:
%
$$
S(z) = a_0z^N+a_1z^{N-1}+\cdots+a_{N-1}z+a_N=0, a_0\neq0
$$
%
%\cdsay{is this for the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$?}
